### 2025-08-06 final-presentation/final.tex

\section{Formalization Of Some proofs}
\subsection*{Defining Natural Numbers} 
    \begin{frame}[fragile]
        \frametitle{Eg: Defining Natural Numbers}
        \begin{verbatim}
           data N : Set where 
                Zero : N 
                suc : N -> N
        \end{verbatim}
    \end{frame}

>>>>

\section{Formalization Of Some Proofs}
\subsection*{Defining Natural Numbers} 
    \begin{frame}[fragile]
        \frametitle{Eg: Defining Natural Numbers}
        \begin{verbatim}
           data N : Set where 
                Zero : N 
                suc : N -> N
        \end{verbatim}
    \end{frame}
\subsection*{simple properities  } 
\begin{frame}[fragile]
    \frametitle{Eg: Some mathematical properities }
    \begin{verbatim}
        Equality and Transitivity:

        data _==_ { A : Set } ( x : A ) : A -> Set where
            refl : x == x

        trans : { A : Set } { x y z : A}
            -> x == y
            -> y == z
            -> x == z
            trans refl refl = refl
    \end{verbatim}
\end{frame}
\subsection{Formalization Of DeMorgan's Law} 
\begin{frame}[fragile]
    \frametitle{DeMorgan's Law in agda}
   \footnotesize \begin{verbatim}
DeMorgan’s Law
open import Agda.Primitive using (Level; lzero)
open import Data.Product using (_×_; _,_)
open import Data.Sum using (_⊎_; inj1; inj2)
open import Relation.Nullary using (Dec; yes; no)
open import Data.Empty using (⊥; ⊥-elim)
open import Relation.Nullary.Negation using (¬_)
--One Direction
deMorganOneWay : ∀ {ℓ} {P Q : Set ℓ} → (¬ P) ⊎ (¬ Q) → ¬ (P × Q)
deMorganOneWay (inj1 np) (p , q) = np p
deMorganOneWay (inj2 nq) (p , q) = nq q

    \end{verbatim}

\end{frame}
\begin{frame}[fragile]

    \small \begin{verbatim}
Converse, Requires Non Constructive Assumptions
deMorganOtherWay :
∀ {ℓ} {P Q : Set ℓ}
→ Dec P
→ Dec Q
→ ¬ (P × Q)
→ (¬ P) ⊎ (¬ Q)
deMorganOtherWay (yes p) _ notPQ = inj2 (λ q → notPQ (p , q))
deMorganOtherWay (no np) (yes q) _ = inj1 np
deMorganOtherWay (no np) (no nq) _ = inj1 np -- or inj2 nq
    \end{verbatim}

\end{frame}
\section{ Limitations}
\begin{frame}{}
    \begin{itemize}
        \item Issue while implementing Real Numbers Construcitvely.
        \item Bidirectional Typechecking Algorithm isn't discussed rigorously.

\begin{frame}{References}
\footnotesize
\begin{itemize}
  \item William Howard. \textit{The formula-as-types notion of construction}, 1969.
  \item Per Martin-Löf. \textit{An Intuitionistic Theory of Types}, 1972.
  \item Jan Willem Klop, Alejandro Ríos. \textit{Introduction to Lambda Calculus}, Rojas, 2015.
  \item Herman Geuvers. \textit{Proof Assistants: History, Ideas and Future}, 2009.
  \item Frank Pfenning. \textit{Intuitionistic Logic: Proof Theory}, Lecture Notes, 2004.
 \item Sozeau, M. et al. (2025). \textit{Correct and complete type checking and certified erasure for Coq, in Coq}, J. ACM, 72(1).
  \item Team, R. P. D. (2025). \textit{Rocq Prover Reference Manual: Core Language}. Accessed: 2025-08-05.
\end{itemize}
\end{frame}
